\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-08-25 to-do.tex
incorporate some notes into gamma decreasing in tau section of to-do
add outline of paper w/propositions to to-do list

\section{Make a bigger deal of the idea of \texorpdfstring{$\gamma$}{gamma} decreasing function of tariffs---move out of footnote}
Ethier 2012 for protection decreasing function of $\tau$ [NEED TO REVISIT IN TEXT]. ``The Political-Support Approach to Protection,'' Global Journal of Economics
	\begin{itemize}
		\item Making $W$ quadratic in $\ga$ such as $\ga - \ga^2$ gives a nice interior max
	\end{itemize}

@@

>>>>

\section{Make a bigger deal of the idea of \texorpdfstring{$\gamma$}{gamma} decreasing function of tariffs---move out of footnote}
Ethier 2012 for protection decreasing function of $\tau$ [NEED TO REVISIT IN TEXT]. ``The Political-Support Approach to Protection,'' Global Journal of Economics
\begin{itemize}
	\item Making $W$ quadratic in $\ga$ such as $\ga - \ga^2$ gives a nice interior max
	\item I think what I have already has returns to $e$ decreasing in $\tau$. Don't I show it? If not in this paper, in RoIE paper.
	\item What embodies returns to lobbying?
		\begin{itemize}
			\item $e \rightarrow \ga(e)$ is how lobbying is translated into weight in political process. It's not `returns.'
			\item $\tau$ isn't even returns. $\pi(\tau(e_2)) - \pi(\tau(e_1))$ is returns.
		\end{itemize}
	\item To get returns decreasing in $\tau$, maybe weighting can't be confined to $PS$
\end{itemize}

@@

\newpage
Current structure of paper (August 25, 2016)
\begin{enumerate}
	\item Introduction
	\item Model
	\item Rigid Tariffs with Endogenous Political Pressure
		\begin{itemize}
			\item[3.1] Perfect External Enforcement. Proposition 1: weak bindings and ext. enforcement imply applied tariff = binding and may use binding to encourage or restrain lobbying
			\item[3.2] $\cdot$
				\begin{itemize}
					\item[3.2.1] $\cdot$
					\item[3.2.2] Prop 2: No ext enforcement: self enforcing implies $\tau^a \leq$ optimal binding with external enforcement
				\end{itemize}
		\end{itemize}
	\item Endogenous Political Pressure and the Escape Clause
		\begin{itemize}
			\item[4.1] Strong bindings: no cost when $\ga(e)$ only
			\item[4.2] Side payments: spirit not upheld, but IC
			\item[4.3] $\ga(s,e)$, Prop 3: lower binding never used
			\item[4.4] EC for endogenous politics
		\end{itemize}
	\item Conclusion
\end{enumerate}
